---
title: "Busch_Consulting_Group_Fake_Job_Postings"
author: "Joann Lariza, Anish Gupta, Yingfan He"
date: "2022-11-06"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(jsonlite)
library(ggthemes)
library(readxl)
library(lubridate)
library(sf)
library(mapview)
library(plotly)
library(dplyr)
library(maps)
library(packcircles)
library(reshape2)
library(RColorBrewer)
library(countrycode)
library(ggbeeswarm)
library(rworldmap)
library(tmap)
library(shiny)
library(leaflet)
library(tmaptools)
library(spData)
library(tigris)
library(gganimate)
library(knitr)
library(png)
library(viridis)
library(shinyjs)
library(tidytext)
library(wordcloud)
library(treemapify)

knitr::opts_chunk$set(echo = TRUE)
```

#### Read fake_jobs file
```{r read files}
fake_jobs <- read_csv("fake_job_postingsFRAUDULENTONLYwithlongLat.csv")
#glimpse(fake_jobs)
```

#### Clean file
```{r Clean fake_jobs file}
fake_jobs <- fake_jobs %>%
  # Get country names from countrycode
  mutate(country_name = countrycode(sourcevar = country, "iso2c", destination = "country.name")) %>%
  mutate(longitude = ifelse(is.na(longitude), 0, longitude)) %>%
  mutate(latitude = ifelse(is.na(latitude), 0, latitude))
#glimpse(fake_jobs)
```

### World Map of all Fake Jobs 
```{r World Map of Fake Jobs}
fake_jobs %>%
  mapview(xcol = "longitude", ycol = "latitude", crs = 4269, grid = FALSE, legend = FALSE)
```

#### Number of Fake Jobs by each Country
```{r Number of Fake Jobs by Country}
fake_jobs_by_country <- fake_jobs %>%
  group_by(country_name) %>%
  summarise(fake_job_numbers = n(), na.rm = TRUE) %>%
  select(country_name, fake_job_numbers)

fake_jobs_by_country <- fake_jobs_by_country[!is.na(fake_jobs_by_country$country_name), ]

fake_jobs_by_country<-fake_jobs_by_country %>%
  rename(name = country_name)

#View(fake_jobs_by_country)
```

### Heatmap of all Fake Jobs Worldwide
```{r Heatmap of Fake Jobs Worldwide}
data("World")
World2 <- merge(World, fake_jobs_by_country, by="name")
#View(World2)
World2 <- st_sf(World2)

tm_shape(World2) +
  tm_polygons("fake_job_numbers", contrast=.7, id = "NAME", title = "Heatmap of Fake Jobs Worldwide", palette = "Accent") +
  tmap_mode("view")

```

#### Get Fake Jobs in USA by State
```{r fake jobs USA}
fake_jobs_usa <- fake_jobs %>%
  filter(country_name == "United States") %>%
  rename(STUSPS = state) %>%
  drop_na(STUSPS)

fake_jobs_usa_by_state <- fake_jobs_usa %>%
  group_by(STUSPS) %>%
  summarise(fake_job_numbers = n(), na.rm = TRUE) %>%
  select(STUSPS, fake_job_numbers)
  
#View(fake_jobs_usa)
```

#### Create dataframe for USA fake jobs by States Map
```{r dataframe for USA fake jobs map}
us <- states(class = "sf")
us2 <- merge(us, fake_jobs_usa_by_state, by="STUSPS")
#glimpse(us2)
```

### Heatmap of USA Fake Jobs by State
```{r Map of Fake Jobs by State}
tm_shape(us2) +
  tm_polygons("fake_job_numbers", id = "NAME", title = "Heatmap of Fake Jobs by State", palette = "Reds")
```

#### Prepare data for building a Word Cloud of Job Title keywords
```{r Data prep for Building a Word Cloud}
fake_jobs_title <- fake_jobs %>%
  select(title)


# tokenize
tokens <- fake_jobs_title %>% 
  unnest_tokens(word, title) %>% 
  dplyr::count(word, sort = TRUE) %>% 
  ungroup()

tokens %>%
  head(10)

# remove stop words
data("stop_words")
tokens_clean <- tokens %>%
  anti_join(stop_words)

# remove numbers
nums <- tokens_clean %>% 
  filter(str_detect(word, "^[0-9]")) %>% 
  select(word) %>% 
  unique()

tokens_clean <- tokens_clean %>% 
  anti_join(nums, by = "word")
```

### Word Cloud of Job Title keywords
```{r Create Word Cloud}
# define a nice color palette
pal <- brewer.pal(8,"Dark2")

# plot the 50 most common words
tokens_clean %>% 
  with(wordcloud(word, n, random.order = FALSE, max.words = 50, colors=pal))


```

#### Read fake jobs
```{r read fake jobs}
jobpostings <- read.csv("fake_job_postings.csv")
jobpostings
fake <- read.csv("fake_job_postingsFRAUDULENTONLY.csv")
#fake

```



# Fake Jobs in different industries
```{r fake jobs by industry}
p <- ggplot(fake, aes(fill=fake$required_experience, y=fake$job_id, x=fake$required_education)) + 
  geom_bar(position="stack", stat="identity")
p1 <- p + theme(axis.text.x = element_text(angle = 90))
ggplotly(p1)

```



# Required experience vs. required education (based off of fake job postings)
```{r experience vs. education}
p <- ggplot(fake, aes(x=fake$industry, fill=fake$industry)) + geom_bar() 
p2 <- p + theme(axis.text.x = element_text(angle = 90))
ggplotly(p2)


```



# Salaries within industries (based off of fake job postings)
```{r salaries within industry}
p <- ggplot(fake, aes(x=fake$industry,y=fake$salary,fill=fake$industry)) +
   geom_boxplot()
p3 <- p + theme(axis.text.x = element_text(angle = 90)) + 
  labs(title="Box plot of salary ranges", 
       subtitle="Grouped by industry",
       x="Industry",
       y="Salary")

ggplotly(p3)

```